---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sparse

<!-- badges: start -->
[![R-CMD-check](https://github.com/dylanh713-sds/sparse/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/dylanh713-sds/sparse/actions/workflows/R-CMD-check.yaml)
[![Test coverage](https://raw.githubusercontent.com/dylanh713-sds/sparse/coverage/badges/coverage.svg)](https://github.com/dylanh713-sds/sparse/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

The sparse package provides the `sparse_numeric` class which is a representation
fo a sparse numeric vector. This class comes with associated helper methods to 
do operations on these vectors such as addition, multiplication, etc... 

## Example

To construct a sparse vector, we can convert a dense vector to sparse like so.

```{r}
library(sparse)

dense1 <- c(1, rep(0, 1e7))
dense2 <- c( rep(0, 1e7), 1)
sparse1 <- as(dense1, "sparse_numeric")
sparse2 <- as(dense2, "sparse_numeric")
```

Now with this sparse vector we can perform basic arithmetic operations such as addition,
multiplication, and subtraction.

```{r}
sparse1 - sparse2
sparse1 + sparse2
sparse1 * sparse2
```

We also define other helpers such as the inner product, mean, and standardization.
```{r}
sparse_crossprod(sparse1, sparse2)
mean(sparse1)
s <- standardize(sparse1)
```

Finally we can print and visualize sparse vectors.
```{r}
show(sparse1)
plot(sparse1, sparse2)
```



